Exp1 - Opt w_max and {A,phi)

### 2018-03-11 voltagebudget/analysis/paper_figures.Rmd
tweaks to bound 1 fig

fig1 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=fig2, 
            aes(x=V_osc/V_comp, y=errors*1e3), 
            color="black", size=0.5) +
  labs(x="V_osc/V_comp", y="Error (ms)") -> p2

>>>>

fig1 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=fig2, 
            aes(x=V_osc/V_comp, y=errors*1e3), 
            color="black", size=0.8) +
  labs(x="V_osc/V_comp", y="Error (ms)") -> p2
